Dynein walks like an Imperial AT-ST

### 2018-02-26 papers/paper/paper.tex
Add step alternation/passing plot to paper
Make paper.pdf build.
New data file scheme: static and exponential data files hold data from respective trials, and are used to make plots for paper.pdf.

@@

\input{../../data/paper_histogram_stepping_parameters.tex}

@@

\subsection*{Results}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper-trajectory-plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_length_histogram_paper.pdf}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/stepping_time_histogram_paper.pdf}
\caption{Histogram of duration of steps taken by model.}
\label{fig:timehist}
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/total_step_time_vs_step_length_multiple_seeds}
\caption{Histogram of duration and length of steps taken by model.}
\label{fig:timehist}
\end{figure}

\begin{table}%[tbhp]
\centering
\caption{Parameters used in model simulation.}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\

@@

\begin{figure}%[tbhp]
  \centering
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}

@@

\begin{figure}%[tbhp]
  \centering
\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
    dynein heavy chains superimposed with model motor angles, both
    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
    MT with model binding angle superimposed, from
    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
    bound to an MT with model superimposed, from
    \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}

See schematic in Figure~\ref{fig:modelangles}.

>>>>

\usepackage{subcaption}

@@

\input{../../data/paper_static_stepping_parameters.tex}

@@

\section{Results}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_static_time_vs_length}
\caption{Heatmap of relationship between step length and time.}
\label{fig:duration-length}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

%% \begin{figure}%[tbhp]
%% \centering
%% \includegraphics[width=\linewidth]{../../plots/stepping_analysis_paper.pdf}
%% \caption{Histogram of duration of steps taken by model.}
%% \label{fig:timehist}
%% \end{figure}

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure*}

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\

@@

\begin{figure}[tbhp]
  \centering
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}

@@

\begin{figure}[tbhp]
  \centering
\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
    dynein heavy chains superimposed with model motor angles, both
    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
    MT with model binding angle superimposed, from
    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
    bound to an MT with model superimposed, from
    \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}
